\documentclass[12pt, twoside, a4paper]{article}

\usepackage{ulem}
\usepackage{geometry}
\usepackage[T1]{fontenc}

\geometry{lmargin=1in, rmargin=1in, bmargin=1in, tmargin=1in} % Set all margins to 1 inch

\pagestyle{empty}
\newcommand{\PersonDetails}[5]{
		\textbf{\MakeUppercase{#1}} \par                            % Name
		{R/ at: #2} \par					          % Address Line 1
		#3 \par                                                                        % Address Line 2
		#4 -- #5 						          % City, State - PIN
}

\begin{document}

\vspace*{\fill}

\centerline{\uline{\textbf{\Large RENTAL AGREEMENT}}}

\bigskip

This RENTAL AGREEMENT is made and executed on 30th day of September 2016, (30-09-2016) BETWEEN
\bigskip

\PersonDetails{Shivappa Reddy}{Kada Agrahara}{Anekal Taluk, Sarjapura Hobli}{Bengaluru, Karnataka}{562125}

\pagebreak

hereinafter referred to as the \textbf{``OWNER/LESSOR"} of the FIRST PART, and
\bigskip

\PersonDetails{Sajesh Vijayan}{Kanangattu Puthen Parambil House}{Kangazha, Edayirickapuzha}{Kottayam, Kerala}{686541}

\bigskip
hereinafter referred to as the \textbf{``LESSEE/TENANT"} of the OTHER PART:

\bigskip

And whereas the Lessor is the sole and absolute owner of the residence \textbf{Kada Agrahara, Anekal Taluk, Sarjapura Hobli, Bengaluru - 562125}, he is prepared to let out the same to the above lessee on the following terms and conditions.

\bigskip
\bigskip

{\Large \textbf{\textsc{this agreement witnesses as follows}}}

\begin{enumerate}
\item {The rent, amounting to \textbf{Rs. 4000/- (Rupees Four Thousand only), including water consumption charge}, will take effect from \textbf{01-10-2016 to 01-09-2017} for a period of 11 months.}
\item {The tenant should pay the advance amount of \textbf{Rs. 15000/- (Rupees Fifteen Thousand only)} to the owner by way of cash before the witnesses. This amount shall not carry any interest and the same will be refunded by the owner to the tenant while vacating the rental premises}
\item {The tenant should keep the schedule premises in good and tenantable condition, and in case any damage caused by the tenant, the same should pay for repair, or an equivalent sum could be deducted from the advance paid.}
\item {The tenant should pay the electricity bill to the concerned departmental authorities.}
\item {The tenant should not sublet or under-let the premises to any other person.}
\item {The tenant should use the premises only for residential purpose, and not for any illegal activity.}
\item {The tenant shall provide the owner a notice at least one month prior to vacating the property.}
\item {The tenant shall whitewash the walls, or pay towards the same, or allow the equivalent money to be deducted from the advance paid, when vacating the property.}
\end {enumerate}
\end{document}